Holomorphic field theories and higher algebra

### 2024-10-11 draft.tex
more refs

Examples appear very naturally from topology: for any space $X$ with a basepoint $x$, take the singular chains $C_\bu(\Omega^d X)$ of the $d$-fold based loop space $\Omega^d_x X$.
A much more subtle source of examples was conjectured by Deligne and subsequently proven in many ways \cite{}: 
for any associative algebra $A$, the Hochschild cochain complex ${\rm Hoch}^\bu(A,A)$ can be equipped naturally with an $E_2$-algebra structure.

@@

\owen{Rewrite this first attempt to be more accurate.}

@@

\begin{rmk}
Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
and their version has had great success in algebraic geometry and representation theory,
particularly in the setting of the geometric Langlands program.
Francis, Gaitsgory, and Lurie ported the spirit of this notion into the setting of manifolds,
developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
for questions in algebraic topology.
Motivated by these efforts (and benefiting from conversations as those works were in progress), 
Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
These approaches share a common spirit but have important technical differences.
A detailed comparison between the versions for locally constant factorization algebras exists \owen{good refs?},
but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
(See, however, the last section of \cite{HenKap} for important steps in that direction.)
\end{rmk}

@@

We are now in a position to define factorization algebras,
which are prefactorization algebras whose behavior on large open sets is determined by their behavior on small open sets.
To give a precise description, we introduce a Grothendieck topology due to Michael Weiss~\owen{cite  \cite{Weiss} and it is explained nicely and further developed in \cite{BoavidaWeiss}}.

@@

\begin{thm}[\owen{citations}]
The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
\[
{\rm Hoch}_\bu(A) \simeq \check{C}(\mathfrak{U},\cF_A)
\]
for any Weiss cover of~$S^1$.
\end{thm}

@@

\og{Discuss twist along circle by automorphism of algebra. Forward ref to example later.}

>>>>

Examples appear very naturally from topology: for any space $X$ with a basepoint $x$, take the singular chains $C_\bu(\Omega^d X)$ of the $d$-fold based loop space $\Omega^d_x X$.
A much more subtle source of examples was conjectured by Deligne and subsequently proven in many ways: 
for any associative algebra $A$, the Hochschild cochain complex ${\rm Hoch}^\bu(A,A)$ can be equipped naturally with an $E_2$-algebra structure.

@@

@@

\begin{rmk}
Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
and their version has had great success in algebraic geometry and representation theory,
particularly in the setting of the geometric Langlands program.
Francis, Gaitsgory, and Lurie ported the spirit of this notion into the setting of manifolds,
developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
for questions in algebraic topology.
Motivated by these efforts (and benefiting from conversations as those works were in progress), 
Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
These approaches share a common spirit but have important technical differences.
A detailed comparison between the versions for locally constant factorization algebras exists~\owen{KSW},
but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
(See, however, the last section of \cite{HenKap} for important steps in that direction.)
\end{rmk}

@@

We are now in a position to define factorization algebras,
which are prefactorization algebras whose behavior on large open sets is determined by their behavior on small open sets.
To give a precise description, we introduce a Grothendieck topology due to Michael Weiss, 
which is explained nicely and further developed in~\cite{BoavidaWeiss}.

@@

\begin{thm}[\cite{LurieHA, AF,KSW}]
The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
\[
{\rm Hoch}_\bu(A) \simeq \check{C}(\mathfrak{U},\cF_A)
\]
for any Weiss cover of~$S^1$.
\end{thm}

@@

\owen{Discuss twist along circle by automorphism of algebra. Forward ref to example later.}
